\Title

### 2022-09-13 Grimaldi-etal-BiolCybernetics.tex

In this work, we study the emergence of such spatio-temporal spiking motifs when training a single layer of spiking neurons on a supervised classification task (\seeFig{motionclouds}). We develop a SNN-like method able to learn hetero-synaptic delays to perform motion detection on a synthetic event-based dataset. Because neuromorphic devices are, by design, good candidates to integrate computations with time, we highlight the fact that this event-driven algorithm is transferable to such hardware.
%
\section{Methods}
\label{sec:methods}
%
In a recent study, we have introduced a spiking neural network as a classification model applied to event streams based on Multinomial Logistic Regression (MLR)~\citep{Grimaldi22pami} which extended the HOTS model~\citet{Lagorce17}. This HOTS model represents temporal relationships between events by building ``time surfaces'', 2D images computed using the time difference to the last recorded events. By transforming each event in the stream as a vectorial input, our MLR classifier is able to make a decision for every single event, that is in an online fashion. We have demonstrated on several datasets that it provides with efficient computations resulting in ultra-fast categorization. Additionally, we made a formal bridge between this event-based MLR and a SNN, demonstrating the bio-plausibility of this method and its possible integration to neuromorphic hardware.

>>>>

In this work, we study the emergence of such spatio-temporal spiking motifs when training a single layer of spiking neurons on a supervised classification task (\seeFig{motionclouds}). We develop a SNN-like method able to learn hetero-synaptic delays to perform motion detection on a synthetic event-based dataset. Because neuromorphic devices are, by design, good candidates to integrate computations with time, we highlight the fact that this event-driven algorithm is transferable to such hardware.
%
\section{Methods}
\label{sec:methods}
%
In a recent study, we have introduced a spiking neural network as a classification model applied to event streams based on Multinomial Logistic Regression (MLR)~\citep{grimaldi_robust_2022} which extended the HOTS model~\citet{lagorce_hots_2017}. This HOTS model represents temporal relationships between events by building ``time surfaces'', 2D images computed using the time difference to the last recorded events. By transforming each event in the stream as a vectorial input, our MLR classifier is able to make a decision for every single event, that is in an online fashion. We have demonstrated on several datasets that it provides with efficient computations resulting in ultra-fast categorization. Additionally, we made a formal bridge between this event-based MLR and a SNN, demonstrating the bio-plausibility of this method and its possible integration to neuromorphic hardware.
